Viscous Transport in Eroding Porous Media

### 2019-07-12 docs/transport/erosion_transport.tex
working on intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{s:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A continuation of the methods paper~\cite{qua-moo2018}.
\paragraph{Governing Equations}
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model}.
\end{split}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Continuing with our previous work~\cite{qua-moo2018}, we use a
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) = 
    \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
  \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
is an unknown density function.  In Section~\ref{s:DLPcomplex}, we show
how the Stokes double-layer potential can also be expressed as the sum
of a Laplacian double-layer potential 
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy
\end{align}
and its gradient.  Since the Laplacian double-layer potential can be
written as a Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,
  \label{eqn:laplaceComplex}
\end{align}
where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
the Stokes double-layer potential can be written in terms of Cauchy
integrals and its first derivative.  We also require the derivative of
the Stokes double-layer potential which requires the second derivative
of Cauchy integrals.

@@

The Stokes double-layer potential itself can not represent all solutions
of the incompressible Stokes equations.  Therefore, we complete the
integral equation formulation following the work of Power and
Miranda~\cite{pow-mir1987}.  The completion depends on the Stokeslets
and rotlets
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \quad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, the solution of the Stokes equation is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0(\eeta](\xx), \quad \xx \in \bd\Omega, \\
  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy)\, ds_\yy \quad \ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
    \quad \ell = 1,\ldots,M,
\end{align}
where $\ff$ is the prescribed Dirichlet boundary condition of the
velocity on the outer wall and eroding bodies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
\label{s:DLPcomplex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
All these integrals but the first are a gradient of a Laplace layer
potential.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued density
function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  \label{eqn:cauchy1}
  u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
  u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$

@@

Key variables that are used to characterize porous media flow is the
porosity (area of void space), permeability, and tortuosity.  The
tortuosity, which  quantifies the amount of turning made by a
streamline, is
\begin{align*}
  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
  {\displaystyle\int_{S}u_x(y)\,dy},
\end{align*}
where $S$ is an cross-section perpendicular to the $x$ axis with length
$d$, $\lambda(y)$ is the length of the streamline that is initizalized
at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
the velocity at the $y$-coordinate along $S$.  There have been efforts
to relate the tortuosity to the porosity~\cite{matyka2008tortuosity},
but these results can not be universal since the porosity which depends
on only a single number, the tortuosity is affected by the distribution
of pores within the porous network.  In addition to the hydraulic
tortuosity, a local tortuosity can be used to analyze the local behavior
of a streamline near a body~\cite{matyka2008tortuosity}.  The local
tortuosity of a streamline initialized at $y$ along $S$ is
\begin{align*}
  \tau(y) = \frac{\lambda(y)}{d}.
\end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section, we present the numerical simulations of dense packings
of eroding bodies.  The computational domain $\Omega$ is a rectangle
$[-3,3] \times [-1,1]$ with rounded off corners and we place bodies only
in $[-1,1] \times [-1,1]$.  For all simulations, we discretize $\Gamma =
\bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
on $\Gamma$ is a Hagen-Poiseuille flow.  As the bodies erode, the flow
rate is adjusted to maintain the physical constant pressure drop
boundary condition.  To maintain this pressure drop, we compute the
pressure at near the inlet and outlet at each time step as described in
our previous work~\cite{qua-moo2018}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{s:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Flow-induced erosion deteriorates and reshapes solid material over a
range of scales.  At small scales, such as in groundwater flow,
fluid-mechanical erosion significantly alters the geometry, and
ultimately changes the process of transport through the media.  This
paper extends a quadrature method first outlined by
Barnett~\cite{bar2014} and Barnett, Wu, and
Veerapaneni~\cite{bar-wu-vee2015} to simulate dense packings of eroding
bodies, and then studies coarse-grained variables to characterize
transport in eroded geometries.

The authors previous work~\cite{qua-moo2018} developed numerical methods
to simulate erosion of multiple bodies suspended in a Stokes flow.  The
numerical methods can be broadly separated into two classes---a
high-order method to solve the Stokes equations and the erosion rate in
a complex geometry, and a time stepping method to evolve the eroding
bodies.  The fluid solver uses a second-kind integral equation that is
discretized with the trapezoid rule and solved iteratively with fast
multipole accelerated GMRES, and then the trapezoid rule is used to
compute the shear stress which is required to find the erosion rate.
Once the erosion rate is computed, the bodies are eroded using a {\thL}
coordinate system.  This allows us to maintain a discretization of the
eroding bodies that is equally spaced in arclength, and is guaranteed to
not tangle.

The trapezoid rule is spectrally accurate discretization of integral
equation formulations of the two-dimensional Stokes equation.  However,
at a fixed resolution, the quadrature error of the trapezoid rule is
arbitrarily large near the eroding bodies.  Therefore, simply upsampling
to evaluate the velocity near the eroding bodies is not sufficient.  In
our previous work~\cite{qua-moo2018}, we restrict the proximity between
eroding bodies.  In addition, since we only visualized the velocity and
vorticity in the fluid bulk once per time step, we used an expensive
upsampling scheme.  However, upsampling is not practical when if it is
required at each GMRES iteration or when simulating tracers in the flow.
Therefore, in this paper, we apply a Barycentric quadrature rule to
evaluate the Stokes double-layer potential~\cite{bar-wu-vee2015}.
However, to compute derivatives of the flow, such as the vorticity and
the shear stress, we extend this work to compute the required
derivatives of the double-layer potential.

Since erosion alters the geometry, it also affects coarse-grained
variables.  In this paper, we examine two particular variables that can
be used to understand transport in porous media---the tortuosity and the
anomalous diffusion rates.   The tortuosity quantifies the twisting of
particle trajectories in a medium, and in laminar flow, the tortuosity
is one.  While a porous media often has a large tortuosity, as erosion
creates preferential channels, large numbers of particles become more
laminar, and we expect the tortuosity to decrease.  Anomalous diffusion
is often used to describe transport in a porous media, and it quantifies
the dispersion of particles in the flow.  Again, as the geometry erodes,
particles behave more as a ballistic particle, and we expect less
dispersion.  In this paper, we compute both the tortuosity and the
anomalous diffusion rates of several geometries that form via erosion.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We start by defining the main variables used to model erosion.  We
consider flows inside a confined geometry $\Omega$ that contains $M$
eroding bodies with boundary $\gamma_\ell$.  The boundary of the
bounding geometry is $\Gamma$, and the fluid domain is bounded by $\bd
\Omega = \Gamma \cup \gamma_1 \cup \cdots \cup \gamma_M$.  On each
eroding body, $\nn$ is the normal vector pointing into the body, and
$\ss$ is the unit tangent vector pointing in the counterclockwise
direction.  The normal vector on $\Gamma$ is the outward unit normal.
Neglecting inertial forces, the governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model}.
\end{split}
\end{equation}
Here, $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
prescribed Hagen-Poiseuille velocity field, and
\begin{align}
  \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
  \label{eqn:shearStress}
\end{align}
is the shear stress on the eroding bodies.  Continuing with our previous
work~\cite{qua-moo2018}, we use a double-layer potential formulation for
the velocity $\uu$.  The double-layer potential is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) = 
    \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
  \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
is an unknown density function.  The Stokes double-layer potential
itself can not represent all solutions of the incompressible Stokes
equations.  Therefore, we complete the integral equation formulation
following the work of Power and Miranda~\cite{pow-mir1987}.  The
completion depends on the Stokeslets and rotlets
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \quad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, the solution of the Stokes equation is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0(\eeta](\xx), \quad \xx \in \bd\Omega, \\
  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy)\, ds_\yy \quad \ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
    \quad \ell = 1,\ldots,M,
\end{align}
where $\ff$ is the prescribed Dirichlet boundary condition of the
velocity on the outer wall and eroding bodies.  Then, once the unknown
density function is computed, the shear stress is found by first
computing the deformation tensors of the double-layer potential,
Stokeslets, and rotlets, and then forming the shear stress as defined in
equation~\eqref{eqn:shearStress}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
\label{s:DLPcomplex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the trapezoid rule to discretize the double-layer
potential~\eqref{eqn:stokesDLP}, and to compute its deformation tensor,
results in large quadrature errors if $\xx$ is close to $\bd\Omega$.  We
apply a quadrature method that is constructed in terms of holomorphic
functions, so we must first write all the layer potentials in terms of
Cauchy integrals and their derivatives.  The first step is to write the
Stokes double-layer potential as the sum of a Laplacian double-layer
potential
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy,
\end{align}
and its gradient.  One such decomposition is
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
Next, since the Laplacian double-layer potential can be written as the
Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,
  \label{eqn:laplaceComplex}
\end{align}
where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
the Stokes double-layer potential can be written in terms of Cauchy
integrals and its first derivative.

We also require the derivative of
the Stokes double-layer potential which requires the second derivative
of Cauchy integrals.

@@

The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
All these integrals but the first are a gradient of a Laplace layer
potential.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued density
function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  \label{eqn:cauchy1}
  u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
  u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$

@@

Key variables that are used to characterize porous media flow is the
porosity (area of void space), permeability, and tortuosity.  The
tortuosity, which  quantifies the amount of turning made by a
streamline, is
\begin{align*}
  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
  {\displaystyle\int_{S}u_x(y)\,dy},
\end{align*}
where $S$ is an cross-section perpendicular to the $x$ axis with length
$d$, $\lambda(y)$ is the length of the streamline that is initialized
at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
the velocity at the $y$-coordinate along $S$.  There have been efforts
to relate the tortuosity to the porosity~\cite{matyka2008tortuosity},
but these results can not be universal since the porosity which depends
on only a single number, the tortuosity is affected by the distribution
of pores within the porous network.  In addition to the hydraulic
tortuosity, a local tortuosity can be used to analyze the local behavior
of a streamline near a body~\cite{matyka2008tortuosity}.  The local
tortuosity of a streamline initialized at $y$ along $S$ is
\begin{align*}
  \tau(y) = \frac{\lambda(y)}{d}.
\end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section, we present the numerical simulations of dense packings
of eroding bodies.  The computational domain $\Omega$ is a rectangle
$[-3,3] \times [-1,1]$ with rounded off corners and we place bodies only
in $[-1,1] \times [-1,1]$.  For all simulations, we discretize $\Gamma =
\bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
rate is adjusted to maintain the physical constant pressure drop
boundary condition.  To maintain this pressure drop, we compute the
pressure at near the inlet and outlet at each time step as described in
our previous work~\cite{qua-moo2018}.
